Automated topic naming to support analysis of software maintenance activities

### 2010-08-20 icse/icse2011.tex
more abstract

Researchers have used topic modeling and concept location to understand the latent topics of software development artifacts.
These techniques use unsupervised machine-learning algorithms recover topics.
These topics are word-lists and are difficult to distinguish and interpret. 
Topics are not meaningful until they have been named or interpreted.
Current topic labelling approaches are manual, and do not use domain-specific knowledge to improve, contextualize, or describe results for the developers.
We propose a solution: \emph{labelled topic extraction}.
Topics are extracted using Latent Dirichlet Allocation (LDA) from commit-log comments extracted from source control systems such as CVS and BitKeeper. 
Then these topics given labels relating to a generalizable cross-project taxonomy consisting of non-functional requirements (NFRs).
Our approach was evaluated  with experiments and case studies on two large-scale RDBMS projects: MySQl and MaxDB.
Labelled topic extraction produces appropriate, context-sensitive labels relevant to these projects, which provides fresh insight into their evolving software development activities.

>>>>

Researchers have used topic modeling and concept location to understand the latent topics of software development artifacts.
These techniques use unsupervised machine-learning algorithms to recover topics.
These topics are word-lists and are difficult to distinguish and interpret. 
Topics are not meaningful until they have been named or interpreted.
Current topic labelling approaches are manual, and do not use domain-specific knowledge to improve, contextualize, or describe results for the developers.
We propose a solution: \emph{labelled topic extraction}.
Topics are extracted using Latent Dirichlet Allocation (LDA) from commit-log comments extracted from source control systems such as CVS and BitKeeper. 
These topics are given labels relating to a generalizable cross-project taxonomy consisting of non-functional requirements.
Our approach was evaluated  with experiments and case studies on two large-scale RDBMS projects: MySQl and MaxDB.
Labelled topic extraction produces appropriate, context-sensitive labels relevant to these projects, which provides fresh insight into their evolving software development activities.
